Compartiendo datos en Ecología: como añadir (¿más?) valor a tus datos

### 2019-04-24 ms/tables.Rmd
tables

```{r}
library(tidyverse)
library(here)
library(pander)
library(kableExtra)
library(knitr)
library(dplyr)
library(flextable)
library(officer)
library(here)
library(xlsx)
library(openxlsx)
# library(ReporteRs)
```

@@

t1 <- flextable(d1, col_keys = c("Revista", "Ranking","Revista_href"))
tabla1 <- compose(t1, j = 1, value = as_paragraph(hyperlink_text(x= Revista, url = Revista_href)))

@@

%>% 
  compose(j = "CriterioRepo", value = as_paragraph(hyperlink_text(x="CriterioRepo", url = "CriterioRepo_href"))) %>% 
  compose(j = "pd", value = as_paragraph(hyperlink_text(x="pd", url = "pd_href")))

>>>>

```{r}
library(tidyverse)
library(here)
library(pander)
library(kableExtra)
library(knitr)
library(dplyr)
library(flextable)
library(officer)
library(here)
library(openxlsx)
# library(ReporteRs)
```

@@

t1 <- flextable(d1, col_keys = c("Ranking","Revista","Factor.de.Impacto.2017.(JCR,.Clarivate.Analytics,.2018)",                          "Tipo.de.artículo.principal","Obligatoriedad.de.la.política.de.datos",
                                 "CriterioRepo", "pd"))
tabla1 <- compose(t1, j = "Revista", value = as_paragraph(hyperlink_text(x= Revista, url = Revista_href)))

tabla1 <- compose(tabla1, j = "CriterioRepo", value = as_paragraph(hyperlink_text(x="CriterioRepo", url = "CriterioRepo_href")))

  compose(j = "pd", value = as_paragraph(hyperlink_text(x="pd", url = "pd_href")))

tabla1 <- flextable(tabla1, col_keys = c("Ranking","Revista"))

@@

%>%
